Presentation Title

### 2017-08-04 thesis/chapters/ch1-intro.tex
Remove unused files

Using the aforementioned insight,
we explore an alternative consensus model for blockchain systems where transactions themself do not reach consensus,
but nevertheless verifiable at a later stage by any node in the network.
Informally, our system works as follows.
Every node stores its own blockchain and every block is one transaction.
We randomly select nodes in every round, the selected ones are called facilitators.
They reach consensus not on the individual transactions,
but on the state of every chain represented by a single digest, we call this state the checkpoint.
If a checkpoint of some node is in consensus, 
then that node can proof to any other node that it holds a set of transactions that computes (form a chain) to the checkpoint.
This immediately show that those transactions are tamper-proof.
% TODO mention consensus and trade off?

Our main contributions are the following.
\begin{itemize}
    \item We formally introduce a blockchain consensus protocol that uses individual hash chains on every node and achieves
        horizontally scalable (through checkpoint blocks) for the first time.
    \item We formally analyse our consensus protocol to ensure correctness as defined in our architecture.
    \item We implement our consensus protocol with experiment with up to 1200 nodes,
        our results show strong evidence of horizontal scalability.
\end{itemize}

>>>>

Using the aforementioned insight,
we explore an alternative consensus model for blockchain systems where transactions themself do not reach consensus,
but nevertheless verifiable at a later stage by any node in the network.
Informally, our system works as follows.
Every node stores its own blockchain and every block is one transaction.
We randomly select nodes in every round, the selected ones are called facilitators.
They reach consensus not on the individual transactions,
but on the state of every chain represented by a single digest, we call this state the checkpoint.
If a checkpoint of some node is in consensus, 
then that node can proof to any other node that it holds a set of transactions that computes (form a chain) to the checkpoint.
This immediately show that those transactions are tamper-proof.
We call our protocol ``Checkpoint Consensus''.
% TODO mention consensus and trade off?

Our main contributions are the following.
\begin{itemize}
    \item We formally introduce a blockchain consensus protocol---Checkpoint Consensus.
        It uses individual hash chains and checkpoints on every node to achieve
        horizontally scalable for the first time.
    \item We formally analyse Checkpoint Consensus to ensure correctness as defined in our architecture.
    \item We implement Checkpiont Consensus with experiment with up to 1200 nodes,
        our results show strong evidence of horizontal scalability.
\end{itemize}

### 2017-08-04 thesis/chapters/ch3-model.tex
Remove unused files

We design a novel system in order to achieve our ambitious goals outline in~\Cref{ch:problem}.
The system consist of three protocols---the consensus protocol, the transaction protocol and the validation protocol.
It is based on our prior work on TrustChain~\cite{multichain},
where every node independently interact with each other via their own blockchain\footnote{It is originally called MultiChain but the name has changed to TrustChain}.

@@

\section{System overview}
\label{sec:system-overview}
The architecture of our system is visualised in~\Cref{fig:architecture}.
\begin{figure}[h]
\centering
\includegraphics[width=0.7\textwidth]{architecture}
\caption{Overview of the system architecture}
\label{fig:architecture}
\end{figure}
It consist of one data structure---Extended TrustChain, and three protocols.
The protocols have distinct roles which are evident from their names.
They run concurrently and do not interact with each other.
The only synchronisation happens on the Extended TrustChain layer, where all the protocols read and write from it.
We first describe each component individually, starting with Extended TrustChain, and then explain how they fit together.

@@

\subsection{Combined protocol}
\label{sec:combined-protocol}
The final protocol is essentially the concurrent composition of the three aforementioned protocols,
all making use the Extended TrustChain data structure.

>>>>

Our system---Checkpoint Consensus consist of three protocols---the consensus protocol, the transaction protocol and the validation protocol.
It is based on our prior work on TrustChain~\cite{multichain},
where every node independently interact with each other via their own blockchain\footnote{It is originally called MultiChain but the name has changed to TrustChain}.

@@

\section{System overview}
\label{sec:system-overview}
The Checkpoint Consensus architecture is visualised in~\Cref{fig:architecture}.
\begin{figure}[h]
\centering
\includegraphics[width=0.7\textwidth]{architecture}
\caption{Overview of the system architecture}
\label{fig:architecture}
\end{figure}
It consist of one data structure---Extended TrustChain, and three protocols.
The protocols have distinct roles which are evident from their names.
They run concurrently and do not interact with each other.
The only synchronisation happens on the Extended TrustChain layer, where all the protocols read and write from it.
We first describe each component individually, starting with Extended TrustChain, and then explain how they fit together.

@@

\subsection{Combined protocol}
\label{sec:combined-protocol}
The final result is essentially the concurrent composition of the three aforementioned protocols,
all making use the Extended TrustChain data structure.

### 2017-08-04 thesis/chapters/ch4-analysis.tex
Remove unused files

\Cref{theorem:validation-agreement} shows that agreement on CP blocks would lead to agreement on TX blocks when the nodes are running the validation protocol.
Just like in our prior work~\cite{implicitconsensus}, we call this behaviour implicit consensus.
One of the main advantages of our scheme over running a consensus algorithm on all the transactions is that 
the rate of transaction is no longer dependent on the consensus algorithm---ACS.
This enables horizontal scalability where adding new nodes would lead to higher global transaction rate.
In addition, a convenient consequence \Cref{theorem:validation-agreement} is unforgeability.
That is, no polynomial time adversary is able to create two chains $F = \{ \dots, t, c\}$ $F' = \{ \dots, t', c\}$ with correct hash pointers and the same end of chain $c$.
% Another way to think about it is if a transaction can be forged, then it cannot be agreed.

@@

The bound is not tight, but it is useful for for picking parameters.
For some fixed $n$, since $0 \le \alpha \le \lfloor \frac{n-1}{3} \rfloor/n < (\lfloor  \frac{n - 1}{3} \rfloor + 1) / n$,
the probability is maximum when the squared term is minimum at $\alpha = \lfloor \frac{n-1}{3} \rfloor/n$.
The probability is minimum when the squared term is maximum at $\alpha = 0$.
Hence, if $n$ is known, then we can pick a $\alpha$ such that the probability becomes small.
On the other hand, if $\alpha$ is fixed, but small, we may increase $n$ to achieve the same.
To put this into perspective, suppose $n = 1000$ and $\alpha = 1/20$, then the probability to draw more black balls than the threshold is only $2 \times 10^{-48}$.

>>>>

\Cref{theorem:validation-agreement} shows that agreement on CP blocks would lead to agreement on TX blocks when the nodes are running the validation protocol.
Like in our prior work~\cite{implicitconsensus}, we call this behaviour implicit consensus.
One of the main advantages of our scheme over running a consensus algorithm on all the transactions is that 
the rate of transaction is no longer dependent on the consensus algorithm---ACS.
This enables horizontal scalability where adding new nodes would lead to higher global transaction rate.
In addition, a convenient consequence \Cref{theorem:validation-agreement} is unforgeability.
That is, no polynomial time adversary is able to create two chains $F = \{ \dots, t, c\}$ $F' = \{ \dots, t', c\}$ with correct hash pointers and the same end of chain $c$.
% Another way to think about it is if a transaction can be forged, then it cannot be agreed.

A stronger version of the validity definition exists.
That is, if two nodes are making transactions with each other,
then the resulting transaction is always valid in addition to our current validity definition.
Under our purely asynchronous model, we cannot guarantee this stronger version.
Since the adversary can delay any message for any amount of time,
it can make sure all \texttt{tx\_req} messages are delivered in a round later than the round which the message is sent.
Effectively, the transaction pair would always be in different rounds and the validation protocol would not output \emph{valid}.
We believe in a relaxed model, i.e. a weakly synchronous model, a stronger validity definition is possible.

@@

The bound is not tight, but it is useful for for picking parameters.
For some fixed $n$, since $0 \le \alpha \le \lfloor \frac{n-1}{3} \rfloor/n < (\lfloor  \frac{n - 1}{3} \rfloor + 1) / n$,
the probability is maximum when the squared term is minimum at $\alpha = \lfloor \frac{n-1}{3} \rfloor/n$.
The probability is minimum when the squared term is maximum at $\alpha = 0$.
Hence, if $n$ is known, then we can pick a $\alpha$ such that the probability becomes small.
On the other hand, if $\alpha$ is fixed, but small, we may increase $n$ to achieve the same.
To put this into perspective,
suppose $n = 1000$ and $\alpha = 1/5$, i.e. a fifth of the nodes are malicious.
Then the probability to draw more black balls than the threshold is only $2.6 \times 10^{-16}$.

### 2017-08-04 thesis/chapters/ch6-conclusion.tex
Remove unused files

The research question we asked in~\Cref{ch:problem} is the following.
\begin{displayquote}
\emph{Is it possible to design a blockchain consensus protocol that is fault tolerant, scalable and can reach global consensus?}
\end{displayquote}
We answer it in the affirmative and our system achieves all the requirements.
Fault tolerance is guaranteed if $n \ge 3t + 1$ from ACS.
While $t$ may be small compared to the population size $N$,
we show that the probability for the system to fail is low even when $n \ge 3t + 1$ does not hold as long as the proportion of malicious nodes is not close to a third of $N$.
Horizontal scalability is demonstrated both analytically and experimentally.
With 1200 nodes in the network we were able to achieve nearly 5000 TX/s---an order of magnitude improvement over Bitcoin.
Finally, we achieve global consensus on transactions via consensus on checkpoint blocks.

This work is the first step in building a new paradigm for blockchain consensus protocol.
It has the potential to efficiently cultivate trust on the internet in the presence of faults without any central authority.
We hope to improve our design by building a concrete application on top of it.

@@

The fault tolerance property of our system is lower than that of typical blockchain systems,
which usually aim for fewer than 50\%.
For future work, we propose the following two ways to improve fault tolerance.
First, use a reputation mechanism to select facilitators rather than simply selecting them randomly so that faulty nodes are less likely to be selected.
This technique of course heavily depends on the application,
for P2P file sharing systems the reputation score may be the number of bytes contributed to the network.
Second, instead of using ACS we use a proof-of-stake (PoS) scheme which means that nodes with more stake in the system gets more vote.
In an ideal PoS scheme, the system can tolerate any fault if the majority of the stake holders are honest.

>>>>

In this work we introduced an application neutrual blockchain system which we call Checkpoint Consensus.
We add checkpoint block to the existing TrustChain data structure for use in our consensus protocol.
The round based consensus protocol uses ACS as a building block to reach consensus on checkpoint blocks.
The consensus result lets nodes elect new facilitators and create new checkpoint blocks.
Node make transactions via the transaction protocol,
which is adapted from an existing work called True Halves.
We introduce a validation protocol which ensure that if agreed fragments for some transaction exists,
then nodes reach agreement on the validity of that transaction.
The novelty of the validation protocol is that it uses point-to-point communication,
i.e. nodes only validate the transactions of interest,
this enables our horizontal scalability property.

The research question we asked in~\Cref{ch:problem} is the following.
\begin{displayquote}
\emph{Is it possible to design a blockchain consensus protocol that is fault tolerant, scalable and can reach global consensus?}
\end{displayquote}
We answer it in the affirmative.
Fault tolerance is guaranteed if $n \ge 3t + 1$ by using ACS as a building block.
While $t$ may be small compared to the population size $N$,
we show that the probability for the system to fail is low even when $n \ge 3t + 1$ does not hold as long as the proportion of malicious nodes is not close to a third of $N$.
For example, if there the population size is 1000 and 20\% of the nodes are malicious,
the probability for a round to potentially to fail is bounded below $2.6 \times 10^{-16}$.
This probability bound would decrease as the population size increases.
Horizontal scalability property is demonstrated both analytically and experimentally.
Unlike sharding protocols, the property holds regardless of transaction characteristics and needs no parameter selection.
Finally, we achieve global consensus on transactions via consensus on checkpoint blocks.

This work is the first step in building a new paradigm for blockchain consensus protocol.
It has the potential to efficiently cultivate trust on the internet in the presence of faults without a central authority.
We hope to improve our design by building a concrete application on top of it.

@@

The fault tolerance property is adaquate for permissioned systems where nodes have relatively more trust between each other.
However, it is not adaquate for permissionless systems,
which usually aim to tolerate fault that involve a minority of the network,
which can be just shy of 50\%.
For future work, we propose the following two ways to improve fault tolerance.
First, use a reputation mechanism to select facilitators rather than simply selecting them randomly so that faulty nodes are less likely to be selected.
This technique of course heavily depends on the application,
for P2P file sharing systems the reputation score may be the number of bytes contributed to the network.
Second, instead of using ACS we use a proof-of-stake (PoS) scheme which means that nodes with more stake in the system gets more vote.
In an ideal PoS scheme, the system can tolerate any fault if the majority of the stake holders are honest.
